The K2 Bright Star Survey

### 2019-05-09 paper/ms.tex
hogg comments

The objective function $Q_{k,l}$ is the $L_k$ norm on a `lagged' finite difference with a lag parameter $\delta$. For $k = 1$ and $\delta = 1$, $Q_{1,1}$ is the standard Total Variation objective (TV) used in previous halo papers, and can be seen as the L1 norm on the derivative of $f$ or as a discrete approximation to its arc length. The L2 Variation (L2V) with $k=2$ is sometimes referred to in image processing literature as the `smoothness' regularizer, as it seeks to penalize large gradients without necessarily making them sparse. The lag parameter $\delta$ allows for flexibility in modelling systematics occurring at different timescales from cadence-to-cadence, and we investigate its effects below. The order parameter $k$ allows for flexibility in how sensitive we are to normally-distributed versus long-tailed noise. For convenience in the rest of this paper, we will refer to the $k=1$ case as TV, the $k=2$ case as L2V, and the $k=3$ case as L3V.

@@

\begin{figure*}
\plottwo{lag_lc_cdpp.pdf}{lag_lc_sys.pdf}
\caption{Behaviour of long cadence 6.5~hour CDPP (left) and $4 c/d$ systematics power (right) for the quiet dwarf 36~Ophiuchi as a function of lag parameter $\delta$. CDPP shows a minimum for L1 norm and $\delta=10$, i.e. for objective function $Q_{1,10}$.}
\label{cdpps}
\end{figure*}

>>>>

The objective function $Q_{k,l}$ is the $L_k$ norm on a `lagged' finite difference with a lag parameter $\delta$. For $k = 1$ and $\delta = 1$, $Q_{1,1}$ is the standard Total Variation objective (TV) used in previous halo papers \citep[e.g.][]{White2017,Farr2018}, and can be seen as the L1 norm on the derivative of $f$ or as a discrete approximation to its arc length. The L2 Variation (L2V) with $k=2$ is sometimes referred to in image processing literature as the `smoothness' regularizer, as it seeks to penalize large gradients without necessarily making them sparse. The lag parameter $\delta$ allows for flexibility in modelling systematics occurring at different timescales from cadence-to-cadence, and we investigate its effects below. The order parameter $k$ allows for flexibility in how sensitive we are to normally-distributed versus long-tailed noise. For convenience in the rest of this paper, we will refer to the $k=1$ case as TV, the $k=2$ case as L2V, and the $k=3$ case as L3V.

@@

% \begin{figure*}
% \plottwo{lag_lc_cdpp.pdf}{lag_lc_sys.pdf}
% \caption{Behaviour of long cadence 6.5~hour CDPP (left) and $4 c/d$ systematics power (right) for the quiet dwarf 36~Ophiuchi as a function of lag parameter $\delta$. CDPP shows a minimum for L1 norm and $\delta=10$, i.e. for objective function $Q_{1,10}$.}
% \label{cdpps}
% \end{figure*}

\begin{figure*}
\plotone{lag_opt_both.pdf}
\caption{Behaviour of long cadence 6.5~hour CDPP (bottom) and $4 c/d$ systematics power (top) for the quiet dwarf 36~Ophiuchi as a function of lag parameter $\delta$. CDPP shows a minimum for L1 norm and $\delta=10$, i.e. for objective function $Q_{1,10}$.}
\label{cdpps}
\end{figure*}
